### 2014-08-29 paper/paper.Rmd
started working on schools matter, but need the full code matching the poster

```{r load_packages, echo = FALSE, message = FALSE, warning = FALSE, results='hide'}
library(dplyr)
library(stringr)
library(stringr)
library(reshape2)
library(ggplot2)
library(lubridate)
library(ggvis)
library(maps)
library(ggmap)
library(rworldmap)
library (grid)    
library (scales) 
```

@@

```{r dataprep, fig.width=10, fig.height=12, echo = FALSE, message = FALSE, warning = FALSE}
colnames(student2012)[1] <- "name"
# Now add data
student2012$name <- as.character(student2012$name)
student2012$name[student2012$name=="Serbia"] <- "Republic of Serbia"
student2012$name[student2012$name=="Korea"] <- "South Korea"
student2012$name[student2012$name=="Chinese Taipei"] <- "Taiwan"
student2012$name[student2012$name=="Slovak Republic"] <- "Slovakia"
student2012$name[student2012$name=="Russian Federation"] <- "Russia"
student2012$name[student2012$name=="Perm(Russian Federation)"] <- "Russia"
student2012$name[student2012$name=="Hong Kong-China"] <- "Hong Kong S.A.R."
student2012$name[student2012$name=="China-Shanghai"] <- "China"
student2012$name[student2012$name=="China-Macau"] <- "China"
student2012$name[student2012$name=="Connecticut (USA)"] <- "United States of America"
student2012$name[student2012$name=="Florida (USA)"] <- "United States of America"
student2012$name[student2012$name=="Massachusetts (USA)"] <- "United States of America"
student2012$ST06Q01 <- as.numeric(student2012$ST06Q01)
student2012$PV1MATH <- as.numeric(student2012$PV1MATH)
student2012$PV1READ <- as.numeric(student2012$PV1READ)
student2012$PV1SCIE <- as.numeric(student2012$PV1SCIE)
student2012$SENWGT_STU <- as.numeric(student2012$SENWGT_STU)
```

### Teachers, computers, and libraries at school matter

@@

### More TVs yield higher math scores in the developing world, but lower in the developed countries

>>>>

```{r load_packages, echo = FALSE, message = FALSE, warning = FALSE, results='hide'}
library(dplyr)
library(stringr)
library(stringr)
library(reshape2)
library(ggplot2)
library(lubridate)
library(ggvis)
library(maps)
library(ggmap)
library(rworldmap)
library (grid)    
library (scales)
library(doBy)
```

@@

```{r dataprep, echo = FALSE, message = FALSE, warning = FALSE}
colnames(student2012)[1] <- "name"
student2012$name <- as.character(student2012$name)
colnames(school2012)[1] <- "name"
school2012$name <- as.character(school2012$name)

fix_country = function(df) {
df$name = as.character(df$name)
df$name[df$name=="Serbia"] <- "Republic of Serbia"
df$name[df$name=="Korea"] <- "South Korea"
df$name[df$name=="Chinese Taipei"] <- "Taiwan"
df$name[df$name=="Slovak Republic"] <- "Slovakia"
df$name[df$name=="Russian Federation"] <- "Russia"
df$name[df$name=="Perm(Russian Federation)"] <- "Russia"
df$name[df$name=="Hong Kong-China"] <- "Hong Kong S.A.R."
df$name[df$name=="China-Shanghai"] <- "China"
df$name[df$name=="China-Macau"] <- "China"
df$name[df$name=="Connecticut (USA)"] <- "United States of America"
df$name[df$name=="Florida (USA)"] <- "United States of America"
df$name[df$name=="Massachusetts (USA)"] <- "United States of America"

df
}

# Now add data
#student2012$name[student2012$name=="Serbia"] <- "Republic of Serbia"
#student2012$name[student2012$name=="Korea"] <- "South Korea"
#student2012$name[student2012$name=="Chinese Taipei"] <- "Taiwan"
#student2012$name[student2012$name=="Slovak Republic"] <- "Slovakia"
#student2012$name[student2012$name=="Russian Federation"] <- "Russia"
#student2012$name[student2012$name=="Perm(Russian Federation)"] <- "Russia"
#student2012$name[student2012$name=="Hong Kong-China"] <- "Hong Kong S.A.R."
#student2012$name[student2012$name=="China-Shanghai"] <- "China"
#student2012$name[student2012$name=="China-Macau"] <- "China"
#student2012$name[student2012$name=="Connecticut (USA)"] <- "United States of America"
#student2012$name[student2012$name=="Florida (USA)"] <- "United States of America"
#student2012$name[student2012$name=="Massachusetts (USA)"] <- "United States of America"
student2012$ST06Q01 <- as.numeric(student2012$ST06Q01)
student2012$PV1MATH <- as.numeric(student2012$PV1MATH)
student2012$PV1READ <- as.numeric(student2012$PV1READ)
student2012$PV1SCIE <- as.numeric(student2012$PV1SCIE)
student2012$SENWGT_STU <- as.numeric(student2012$SENWGT_STU)

school2012 = fix_country(school2012)
student2012 = fix_country(student2012)
```

### Teachers, computers, and libraries at school make a difference in math scores

```{r shortages, echo = FALSE, message = FALSE, warning = FALSE}
school2012.sub = school2012[, c(1, 6, 34, 35, 40, 45, 46, 47, 48, 49, 50, 51)] #%>% select(name, SCHOOLID, SC11Q02, SC11Q03, SC14Q02, SC14Q07, SC14Q08, SC14Q09, SC14Q10, SC14Q11, SC14Q12, SC14Q13)
student2012.sub = student2012[, c(1, 6, 501, 541, 546, 634)] #%>% select(name, SCHOOLID, PV1MATH, PV1READ, PV1SCIE)

scores_by_school = summarise(group_by(student2012.sub, name, SCHOOLID), mmath = mean(PV1MATH), 
                                      mread = mean(PV1READ), msci = mean(PV1SCIE))

df = scores_by_school %>% left_join(school2012.sub)
df2 <- summarise(group_by(df, name, SC14Q02), mmath2 = mean(mmath))
qplot(SC14Q02, mmath2, data = df2, facets = ~name)
df3 <- summarise(group_by(df, name, SC14Q10), mmath2 = mean(mmath))
qplot(SC14Q10, mmath2, data = df3, facets = ~name)
```

@@

***Need to get this code working

```
# Out of School Study time
b1 <- summaryBy(data=student2012, pvM + pvR + pvS+ ST57Q01+ ST57Q02 +ST57Q03+ ST57Q04+ ST57Q05+ ST57Q06 ~CNT,FUN=mean, na.rm=T)
names(b1) <- c("CNT","pvM","pvR","pvS","ST57Q01", "ST57Q02","ST57Q03", "ST57Q04", "ST57Q05", "ST57Q06" )
# Out of school study time (total hours HW)
b1$CNT <- reorder(factor(b1$CNT),b1$pvS, mean)
b2 <- melt(b1[,c("CNT","pvM","pvR","pvS")],id="CNT")
b2 <- cbind(b2, b1[match(b2$CNT,b1$CNT), 5:10])
qplot(CNT, value,color=variable,size=ST57Q01, data = b2)+ coord_flip()
head(b2)
qplot(ST57Q01, value,color=variable,size=ST57Q02, data = b2)+ coord_flip()+facet_wrap(~CNT)

student.sub <- studschool[,c("name","pvM","pvR","pvS","ST57Q01","OECD","SC03Q01")]
study <- melt(student.sub,id=c("name","ST57Q01","OECD","SC03Q01"))
names(study) <- c("Country","HomeworkHours","OECD","AREA","Subject","Score")
levels(study$Subject) <- c("Math","Reading","Science")
p <- ggplot(data = study, aes(HomeworkHours,Score,colour=Subject) )+xlim(0,20)+facet_wrap(~Country)+stat_smooth(se=F)+ xlab("Out-of-School Study Hours")
#ggsave(p,file="studytime.pdf",height=13,width=13)
p <- ggplot(data=student.sub, aes(ST57Q01, ..density..)) + geom_histogram(binwidth=5) + xlab("Out-of-School Study Hours") +xlim(0,30)
ggsave(p,file="HistHWschool.pdf",width=8,height=6)

student.sub <- studschool[,c("name","pvM","ST57Q01","SC03Q01")]
study <- student.sub
names(study) <- c("Country","Math","HomeworkHours","Schoolplace")

p <- ggplot(data = study, aes(HomeworkHours,Math,colour=Schoolplace) )+xlim(0,20)+facet_wrap(~Country)+stat_smooth(se=F)
#ggsave(p,file="studytime.pdf",height=13,width=13)
p <- ggplot(data=student.sub, aes(ST57Q01, ..density..)) + geom_histogram(binwidth=5) + xlab("Out-of-School Study Hours") + facet_grid(SC03Q01~.) +xlim(0,30)
```
### More TVs yield higher math scores in the developing world, but lower in the developed countries
